---
title: "A systematic review of short-term and working memory abilities in children with intellectual disability; to what extent do the result support the delay or difference hypotheses? "
author: "Cris"
date: "Last Updated: `r format(Sys.time(), '%d, %B, %Y at %H:%M')`"
output: md_document
---

```{r import libraries, include=FALSE, warning=FALSE}
library(metafor)
library(readxl)
library(janitor)
library(reshape)
library(metafor)
library(metaviz)
library(readr)
library(ggplot2)
library(ggthemes)
library(patchwork)
library(TOSTER)
library(dplyr)
library(tidyr)
library(devtools)
library(ggrepel)
# devtools::install_github("MathiasHarrer/dmetar")
library(dmetar)
library(naniar)
library(skimr)
library(psych)
library(utils)
library(pwr)
library(zcurve)
```

```{r create visualization functions from dsquintana, include=FALSE, warning=FALSE}

ma_pipe_sei <-
  function(dat,
           true_effect,
           rep_upper,
           rep_lower,
           analysis_title,
           plot = TRUE) {
#    dat <- read.csv(dat) # Read the file 
     res <- rma.mv(yi, vi, random = list(~ 1 | effectsize_id, ~1 | study_id), 
                          tdist = TRUE, data = stats_test) # Perform a meta-analysis with restricted-max likelihood v estimator
    rep_se <-
      ((rep_upper) - (rep_lower)) / (2 * 1.96) # Calculate SE for the summary effect
    sink("/dev/null")
    et <- TOSTmeta(
      ES = true_effect,
      se = rep_se,
      low_eqbound_d = -0.34,
      high_eqbound_d = 0.34,
      plot = TRUE
    ) # Perform an equivalence test
    # et <- data.frame(matrix(unlist(et), nrow=length(et), byrow=TRUE))
    et <- as.data.frame(et[-13])
    et <- mutate(et, Analysis = analysis_title) # Calculate median power
    sink()
    if (plot) {
      effect_size <- et$ES
      et <- as.data.frame(et)
      et_plot <-
        ggplot(et,
               aes(
                 x = "",
                 y = ES,
                 ymin = low_eqbound_d,
                 ymax = high_eqbound_d
               )) +
        geom_hline(aes(yintercept = 0), linetype = 'solid', size = 0.5) +
        geom_linerange(size = 5,
                       colour = "#00AFBB",
                       alpha = 0.5) +
        annotate(
          geom = "point",
          x = "",
          y = effect_size,
          color = "black",
          shape = 18,
          size = 4
        ) +
        theme(axis.text.x = element_text(size = 8)) +
        coord_flip() +
        theme_minimal() +
        theme(strip.text = element_text(
          size = 8,
          face = "bold",
          angle = 90
        )) +
        theme(strip.background = element_rect(colour = "black", fill = "white")) +
        theme(axis.title.y = element_text(face = "bold", size = 12)) +
        theme(axis.title.x = element_text(face = "bold", size = 12)) +
        theme(axis.title.y = element_blank()) +
        ylab(expression("Effect size"))
      et_plot <-
        et_plot + geom_linerange(aes(ymin = UL_CI_ZTEST, ymax = LL_CI_ZTEST), size = 0.5)
      et_plot <-
        et_plot + geom_linerange(aes(ymin = UL_CI_TOST, ymax = LL_CI_TOST),
                                 size = 1.5,
                                 colour = "black")
      et_plot # Creates an equivalence test plot
    }
    
    value <- list(
      res = res,
      dat = dat,
      et = et,
      et_plot = et_plot
    ) # Create a list of output objects
    attr(value, "class") <- "ma_pipe_sei"
    value
  }


# This function takes equivalence test results from the first function to create an equivalence test forest plot

combine_et <-
  function(dat){
    et_plot_combine <-
      ggplot(dat,
             aes(
               x = reorder(Analysis, -ES),
               y = ES,
               ymin = -0.6,
               ymax = 0.6
             )) +
      geom_rect(xmin = -Inf, ymin = -0.2, xmax = Inf, ymax = 0.2,
                fill = "#800020", alpha = 0.17) +
      geom_rect(xmin = -Inf, ymin = -0.5, xmax = Inf, ymax = 0.5,
                fill = "#800020", alpha = 0.1) +
      geom_rect(xmin = -Inf, ymin = -0.8, xmax = Inf, ymax = 0.8,
                fill = "#800020", alpha = 0.05) +
      geom_point(color = "black",
                 shape = 18,
                 size = 4) +
      theme(axis.text.x = element_text(size = 8)) +
      coord_flip() +
      theme_minimal() +
      theme(strip.text = element_text(
        size = 8,
        face = "bold",
        angle = 90
      )) +
      theme(strip.background = element_rect(colour = "black", fill = "white")) +
      theme(axis.title.y = element_text(face = "bold", size = 12)) +
      theme(axis.title.x = element_text(face = "bold", size = 12)) +
      theme(axis.title.y = element_blank()) +
      ylab(expression("Effect size"))
    et_plot_combine <-
      et_plot_combine + geom_linerange(aes(ymin = UL_CI_ZTEST, ymax = LL_CI_ZTEST), size = 0.5)
    et_plot_combine <-
      et_plot_combine + geom_linerange(aes(ymin = UL_CI_TOST, ymax = LL_CI_TOST),
                                       size = 1.5,
                                       colour = "black")
    et_plot_combine <-
      et_plot_combine + scale_y_continuous(breaks=c(-.8, -.5,-.2, 0, .2, 0.5, 0.8))
    et_plot_combine <-
      et_plot_combine + geom_hline(yintercept=0, linetype="dashed", color = "black")
    et_plot_combine # Creates an equivalence test plot
  }

```

```{r data reading and cleaning, include=FALSE, warning=FALSE}
data <- read_excel("datafile_broader_ef.xlsx")
data <- clean_names(data)
data <- data[!duplicated(data), ]
# colnames(data)[13] <- 'yi'

columns_of_interest <- c('study_year', 'n_id','age_id', 'mean_ma_id', 
                         'sd_ma_id', 'iq_id', 'n_magroup', 'age_magroup',
                         'mean_ma_magroup', 'iq_magroup',
                         'mean_id', 'mean_magroup', 'sd_id','sd_magroup')
  # c('year', 'sample_size_id_n', 'chronological_age_id_m', 'chronological_age_id_sd',
  #                        'mental_age_id_m', 'mental_age_id_sd',
  #                        'iq_id_m', 'iq_id_sd',
  #                        'sample_size_controls_n',  'chronological_age_controls_m', 'chronological_age_controls_sd',
  #                        'mental_age_controls_m', 'mental_age_controls_sd',
  #                        'iq_controls_m', 'iq_controls_sd', 
  #                        'task_1_mean_control_group','task_1_mean_id_group', 'task_1_sd_control_group',
  #                        'task_1_sd_id_group', 'task_1_n_control_group','task_1_n_id_group',
  #                        'task_2_mean_control_group','task_2_mean_id_group', 'task_2_sd_control_group',
  #                        'task_2_sd_id_group', 'task_2_n_control_group','task_2_n_id_group'
  #                        )

data[, columns_of_interest] <- lapply(data[, columns_of_interest], as.numeric)

stats_test <- escalc(
    m2i = mean_magroup,
    m1i = mean_id,
    sd2i = sd_magroup,
    sd1i = sd_id,
    n2i = n_magroup,
    n1i = n_id,
    data = data,
    append = TRUE,
    measure = 'SMD1H'
  )
stats_test$sei <- sqrt(stats_test$vi)
# stats_test_2 <- escalc(
#     m2i = task_2_mean_control_group,
#     m1i = task_2_mean_id_group,
#     sd2i = task_2_sd_control_group,
#     sd1i = task_2_sd_id_group,
#     n2i = task_2_n_control_group,
#     n1i = task_2_n_id_group,
#     data = data,
#     append = TRUE,
#     measure = 'SMD1H'
#   )

#ma_model <- rma(yi, vi, data = stats_test)
# ma_model_2 <- rma(yi, vi, data = stats_test_2)
```

## Aim

The aim of the study is to investigate if short-term and working memory abilities exhibit a developmentally delayed or developmentally different pattern in children with ID. This will be done by an overall analysis and subgroup analyses based on type of memory (short-term or working memory), aetiology of ID (familial or organic). In addition, the overall analysis will also be repeated with level of IQ as a moderator.

### Aims and Research questions

The aim of the study is to investigate if short-term and working memory abilities exhibit a developmentally delayed or developmentally different pattern in children with ID.  This will be done by an overall analysis and subgroup analyses based on the type of memory (short-term or working memory) and the aetiology of ID (familial or organic). In addition, the overall analysis will also be repeated with the level of the severity of the intellectual disability as a moderator. 

Our research questions are: 

1. Do short-term and working memory abilities exhibit a developmentally delayed or developmentally different pattern in children with ID (compared to mental age-matched groups)? 

2. Are these results consistent across the aetiology (familial and organic) of ID or level of IQ? 

For research question 1, we cannot make a prediction as to whether there will be significant differences in short-term and working memory abilities between children with ID and a mental-age-matched comparison group. However, we will use equivalence testing to find out whether within the literature, there is significant statistical evidence to support the delay and the difference hypotheses. Different statistical outcomes and possible conclusions are further described in method section below. For research question 2, we hypothesise, that both IQ and ID origin will significantly moderate STM and WM performance.  

## Methods
### Data extraction

We extracted data from stuff

### Statistical analysis

We tested the difference in performance moderating for type of task and also for type of ID

### Equivalence testing
Yes

## Results

### Descriptives
We conducted and reported this systematic review according to NIRO-SR guidelines for conducting and reporting systematic reviews of non-intervention research (REF). See table X for descriptives of the obtained studies.

```{r data descriptives, warning=FALSE}
skim_data <- skim(data[, columns_of_interest])
skim_data

missing_summary <- miss_var_summary(data[, columns_of_interest])
iq_missing <- missing_summary[missing_summary$variable == "iq_id", "pct_miss"][[1]]
iq_ma_missing <- missing_summary[missing_summary$variable == "iq_magroup", "pct_miss"][[1]]
```

<!---
For both groups, we extracted the IQ scores, number of participants, mean and SD of the performance in the tasks, and the mean and SD of the chronological and mental age. The variable with the most missing data was `r #missing_summary[1, 1]` with `r #missing_summary[1,3]`% data missing. IQ scores for the ID group were missing `r #print(iq_missing)`%, and for the MA group, `r #print(iq_ma_missing)`% of IQ scores were missing.
-->

```{r descriptives, warning=FALSE}
missing_data <- vis_miss(data[,columns_of_interest])
missing_data
```

```{r power, warning=FALSE}

power_median <- pwr::pwr.t2n.test(n1 = 71, n2 = 62, power = 0.80, sig.level = 0.05, alternative = c("greater")) #taken from the largest study (Palmqvist, 2020) in the Spaniol & Danielsson MA

power_median$d

pam_g <- escalc("SMD1", m1i = 5.9, m2i = 7, sd1i = 2.3, sd2i = 1.8, n1i = 71, n2i = 62) #taken from the Palmqvist (2020) working memory task scores

```

### Statistical analysis

We are performing a multilevel meta-analysis of memory span.
```{r tests type of EF}
res_inhibition <- rma.mv(yi, vi, random = list(~ 1 | effectsize_id, ~1 | study_id), 
                          tdist = TRUE, data = stats_test) 

dat.comp <- data.frame(estimate = c(coef(res_inhibition)), 
                       stderror = c(res_inhibition$se),
                       tau2     = c(res_inhibition$tau2))
dfround(dat.comp, 3)

```

```{r plots memory span, fig.dim = c(15, 20)}

# Compute confidence intervals and format labels

df <- stats_test[, c('cite', 'yi', 'sei', 'n_magroup', 'n_id')]
  
df$cite <- paste0(df$cite, '.', ave(df$cite, df$cite, FUN = seq_along))
  df <- df %>%
    mutate(
      lower = yi - 1.96 * sei,  
      upper = yi + 1.96 * sei,  
      ci_text = paste0(round(yi,2), "  [", round(lower, 2), ", ", round(upper, 2), "]")
    )
FE_model <- paste0('RE Model for the memory span outcome')
  df <- df %>%
    arrange(yi)
  df_2 <- data.frame(cite = FE_model, 
                     yi = res_inhibition['b'], 
                     sei = res_inhibition['se'], 
                     n_magroup = NA_integer_,
                     n_id = NA_integer_, 
                     lower= res_inhibition['ci.lb'], 
                     upper = res_inhibition['ci.ub'], 
                     ci_text = paste0(round(as.numeric(res_inhibition['b']),2), 
                           "  [", round(as.numeric(res_inhibition['ci.lb']), 2), ", ", 
                           round(as.numeric(res_inhibition['ci.ub']), 2), "]"))
  df <- bind_rows(df, df_2)
  df[, c('yi','sei', 'lower', 'upper')] <- lapply(df[, c('yi','sei', 'lower', 'upper')], as.numeric)
  df$desired_order <- seq(dim(df)[1],1)
  p_right <- ggplot(df, aes(y = reorder(cite, desired_order))) +
    geom_point(aes(x=yi), size = 3, shape=15, color = "darkred") +  
    geom_errorbarh(aes(xmin = lower, xmax = upper), height = 0.2, color = "grey") +  
    labs(
      x = "Effect Size (Hedges' g)",
      y = "Study",
      caption = "Error bars represent 95% confidence intervals"
    )   + theme(axis.line.y = element_blank(),
                axis.ticks.y= element_blank(),
                axis.text.y= element_blank(),
                axis.title.y= element_blank(),
                panel.background = element_rect(fill = "white"
                )) + coord_cartesian(xlim = c(min(df$lower), max(df$upper)), ylim = c(0,dim(df)[1] + 1))
  p_left <- ggplot(df, aes(y = reorder(cite, desired_order))) + labs(x = '') +
    geom_text(aes(x = 0, label = cite), hjust = 0, fontface = "bold") +
    annotate(geom="text", x=0.3, y=dim(df)[1] + 1, label="Study", fontface = "bold") +
    geom_text(aes(x = 0.8, label = n_id), hjust = 0) +
    annotate(geom="text", x=0.8, y=dim(df)[1] + 1, label="N (ID)", fontface = "bold") +
    geom_text(aes(x = 1, label = n_magroup), hjust = 0) +
    annotate(geom="text", x=1, y=dim(df)[1] + 1, label="N (Control)", fontface = "bold") +
    geom_text(
      aes(x = 1.3, label = ci_text),
      hjust = 0
    ) +
    annotate(geom="text", x=1.4, y=dim(df)[1] + 1, label="Hedges' g [95% CI]", fontface = "bold") +
    theme_void() +
    coord_cartesian(xlim = c(0, 2), ylim = c(0,dim(df)[1] + 1))
  
  layout <- c(
    area(t = 0, l = 0, b = dim(df)[1], r = 5), 
    area(t = 0, l = 6, b = dim(df)[1], r = 8) 
  )
  print(p_left + p_right + plot_layout(design = layout))


```

#### Moderator analyses
Moderating type of ID origin for memory span.
```{r tests type of ID}
#subgroup analysis (RE meta-analysis of each group)
res_DS <- rma.mv(yi, vi, random = list(~ 1 | effectsize_id, ~1 | study_id),
                          subset = group_id == "DS",
                          tdist = TRUE, data = stats_test) # this will be our organic origin
res_NSID <- rma.mv(yi, vi, random = list(~ 1 | effectsize_id, ~1 | study_id),
                          subset = group_id == "NSID",
                          tdist = TRUE, data = stats_test) # this will be our non-specific origin


dat.comp <- data.frame(alloc    = c("DS", "NSID"
                                    ), 
                       estimate = c(coef(res_DS), coef(res_NSID)
                                    ), 
                       stderror = c(res_DS$se, res_NSID$se
                                    ),
                       tau2     = c(res_DS$tau2, res_NSID$tau2
                                   )
                       )
dfround(dat.comp, 3)

#fixed effects meta-analysis of the subgroup estimates
# taken from: https://www.metafor-project.org/doku.php/tips:comp_two_independent_estimates#separate_meta-analyses
rma(estimate, sei=stderror, mods = ~ alloc, method="FE", data=dat.comp, digits=3)

```

```{r plots type of ID, , fig.dim = c(15, 20)}
id_tests <- t(data.frame(DS = c(res_DS$b, res_DS$se,res_DS$ci.lb, res_DS$ci.ub),
                         NSID = c(res_NSID$b, res_NSID$se,res_NSID$ci.lb, res_NSID$ci.ub),
                         row.names = c('b', 'se', 'ci.lb', 'ci.ub')))
for (id in c('DS', 'NSID'
            )
     ){
  df <- stats_test[stats_test$group_id == id, c('cite', 'yi', 'sei', 'n_magroup', 'n_id')]
  
  # Compute confidence intervals and format labels
  
  df$cite <- paste0(df$cite, '.', ave(df$cite, df$cite, FUN = seq_along))
  df <- df %>%
    mutate(
      lower = yi - 1.96 * sei,  
      upper = yi + 1.96 * sei,  
      ci_text = paste0(round(yi,2), "  [", round(lower, 2), ", ", round(upper, 2), "]")
    )
  FE_model <- paste0('RE Model for ', id, ' group')
  df <- df %>%
    arrange(yi)
  df <- rbind(df, c(FE_model, id_tests[id,'b'], id_tests[id,'se'], '','', 
                    id_tests[id,'ci.lb'], id_tests[id,'ci.ub'], 
                    paste0(round(id_tests[id,'b'],2), 
                           "  [", round(id_tests[id,'ci.lb'], 2), ", ", 
                           round(id_tests[id,'ci.ub'], 2), "]")))
  df[, c('yi','sei', 'lower', 'upper')] <- lapply(df[, c('yi','sei', 'lower', 'upper')], as.numeric)
  df$desired_order <- seq(dim(df)[1],1)
  p_right <- ggplot(df, aes(y = reorder(cite, desired_order))) +
    geom_point(aes(x=yi), size = 3, shape=15, color = "darkred") +  
    geom_errorbarh(aes(xmin = lower, xmax = upper), height = 0.2, color = "grey") +  
    labs(
      x = "Effect Size (Hedges' g)",
      y = "Study",
      caption = "Error bars represent 95% confidence intervals"
    )   + theme(axis.line.y = element_blank(),
                axis.ticks.y= element_blank(),
                axis.text.y= element_blank(),
                axis.title.y= element_blank(),
                panel.background = element_rect(fill = "white"
                )) + coord_cartesian(xlim = c(min(df$lower), max(df$upper)), ylim = c(0,dim(df)[1] + 1))
  p_left <- ggplot(df, aes(y = reorder(cite, desired_order))) + labs(x = '') +
    geom_text(aes(x = 0, label = cite), hjust = 0, fontface = "bold") +
    annotate(geom="text", x=0.3, y=dim(df)[1] + 1, label="Study", fontface = "bold") +
    geom_text(aes(x = 0.8, label = n_id), hjust = 0) +
    annotate(geom="text", x=0.8, y=dim(df)[1] + 1, label="N (ID)", fontface = "bold") +
    geom_text(aes(x = 1, label = n_magroup), hjust = 0) +
    annotate(geom="text", x=1, y=dim(df)[1] + 1, label="N (Control)", fontface = "bold") +
    geom_text(
      aes(x = 1.3, label = ci_text),
      hjust = 0
    ) +
    annotate(geom="text", x=1.4, y=dim(df)[1] + 1, label="Hedges' g [95% CI]", fontface = "bold") +
    theme_void() +
    coord_cartesian(xlim = c(0, 2), ylim = c(0,dim(df)[1] + 1))
  
  layout <- c(
    area(t = 0, l = 0, b = dim(df)[1], r = 5), 
    area(t = 0, l = 6, b = dim(df)[1], r = 8) 
  )
  print(p_left + p_right + plot_layout(design = layout))
  Sys.sleep(2)
}


```


### Equivalence testing
The studies looked at different types of executive functions (CHANGE THIS LATER TO SUIT OUR OWN ANALYSIS). In the next table you can see the extracted descriptives separated by executive function.

```{r descriptives ef, warning=FALSE}
describeBy(data[,columns_of_interest], data$ef_type)
```

Equivalence testing for the different types of tasks.

```{r equivalence test plots}
# Overall meta-analyses of STM and WM
inhibition <- stats_test[stats_test$ef_type == 'inhibition',]
inhibition_model <- rma(yi, vi, data = inhibition)
inhibition_results <- ma_pipe_sei(
  inhibition,
  true_effect = inhibition_model$b,
  rep_lower = inhibition_model$ci.lb,
  rep_upper = inhibition_model$ci.ub,
  analysis_title = "Short-term memory tasks",
  plot = TRUE
)

inhibition_et_dat <- inhibition_results$et

# Subgroup analyses for each outcome (here only presented one)
inhibition_DS <- stats_test[stats_test$ef_type == 'inhibition' & stats_test$group_id == "DS",]
inhibition_model_DS <- rma(yi, vi, data = inhibition_DS)
inhibition_results_DS <- ma_pipe_sei(
  inhibition_DS,
  true_effect = inhibition_model_DS$b,
  rep_lower = inhibition_model_DS$ci.lb,
  rep_upper = inhibition_model_DS$ci.ub,
  analysis_title = "STM tasks for organic origin",
  plot = TRUE
)
inhibition_et_dat_DS <- inhibition_results_DS$et

inhibition_NSID <- stats_test[stats_test$ef_type == 'inhibition' & stats_test$group_id == "NSID",]
inhibition_model_NSID <- rma(yi, vi, data = inhibition_NSID)
inhibition_results_NSID <- ma_pipe_sei(
  inhibition_NSID,
  true_effect = inhibition_model_NSID$b,
  rep_lower = inhibition_model_NSID$ci.lb,
  rep_upper = inhibition_model_NSID$ci.ub,
  analysis_title = "STM tasks for familial origin",
  plot = TRUE
)

inhibition_et_dat_NSID <- inhibition_results_NSID$et

## equivalence forest plot
com1 <- rbind(inhibition_et_dat,
              inhibition_et_dat_DS, inhibition_et_dat_NSID)

com1 <- combine_et(com1)

com1 <- com1 + ggtitle("Summary effect sizes and equivalence bounds") +
  theme(plot.title = element_text(hjust = 0.5))

com1

```

# Moderator analysis
```{r meta-regression}
meta_reg <- rma(m1i = mean_magroup, sd1i = sd_magroup, n1i = n_magroup,
                m2i = mean_id, sd2i = sd_id, n2i = n_id, method = "REML", measure = 'SMD1H',
                mods = ~ iq_id, data=stats_test) #IQ predictor will be mean-centered
summary(meta_reg)

meta_reg_prediction <-predict(meta_reg)

  # Add study labels
  
meta_reg_prediction$cite <- paste0(
  meta_reg$data$cite[!is.na(meta_reg$data$iq_id)], 
  '.', 
  ave(meta_reg$data$cite[!is.na(meta_reg$data$iq_id)], 
      meta_reg$data$cite[!is.na(meta_reg$data$iq_id)], 
      FUN = seq_along))
meta_reg_prediction <- data.frame(meta_reg_prediction)

  meta_reg_prediction <- meta_reg_prediction %>%
    arrange(pred)


  p_right <- ggplot(meta_reg_prediction, aes(y = cite)) +
    geom_point(aes(x=pred), size = 3, shape=15, color = "darkred") +  
    geom_errorbarh(aes(xmin = pi.lb, xmax = pi.ub), height = 0.2, color = "grey") +  
    labs(
      x = "Prediction",
      y = "Study",
      caption = "Error bars represent prediction boundaries"
    )   + theme(axis.line.y = element_blank(),
                axis.ticks.y= element_blank(),
                axis.text.y= element_blank(),
                axis.title.y= element_blank(),
                panel.background = element_rect(fill = "white"
                )) + coord_cartesian(xlim = c(min(meta_reg_prediction$pi.lb), max(meta_reg_prediction$pu.ub)), ylim = c(0,dim(meta_reg_prediction)[1] + 1))
  p_left <- ggplot(meta_reg_prediction, aes(y = cite)) + labs(x = '') +
    geom_text(aes(x = 0, label = cite), hjust = 0, fontface = "bold") +
    annotate(geom="text", x=0.3, y=dim(meta_reg_prediction)[1] + 1, label="Study", fontface = "bold") +
    annotate(geom="text", x=1.4, y=dim(meta_reg_prediction)[1] + 1, label="Prediction", fontface = "bold") +
    theme_void() +
    coord_cartesian(xlim = c(0, 2), ylim = c(0,dim(meta_reg_prediction)[1] + 1))
  
  layout <- c(
    area(t = 0, l = 0, b = dim(meta_reg_prediction)[1], r = 5), 
    area(t = 0, l = 6, b = dim(meta_reg_prediction)[1], r = 8) 
  )
  print(p_left + p_right + plot_layout(design = layout))
  Sys.sleep(2)


```


## Sensitivity analysis
```{r sensitivity-analysis}
# Cook's distance
sens_inh <- cooks.distance.rma.mv(res_inhibition)
plot(sens_inh, type="o", pch=19, xlab="Observed Outcome", ylab="Cook's Distance")

## "leave-one-out" analysis with dfbetas value for dependent effect size multilevel analyses
loneo <- dfbetas(res_inhibition) %>% as.matrix()
plot(loneo, type="o", pch=19, xlab="Observed Outcome", ylab="DFBETAS Value")

## sensitivity analysis for the inclusion criteria
#subgroup analysis (RE meta-analysis of each group)
stats_test <- stats_test %>% mutate(group_inclusion_criteria = sample(c("group_a","group_b","group_c","group_d"), n(), replace = TRUE))

res_a <- rma.mv(yi, vi, random = list(~ 1 | effectsize_id, ~1 | study_id),
                          subset = group_inclusion_criteria == "group_a",
                          tdist = TRUE, data = stats_test) # studies reported every participant’s IQ score
res_b <- rma.mv(yi, vi, random = list(~ 1 | effectsize_id, ~1 | study_id),
                          subset = group_inclusion_criteria == "group_b",
                          tdist = TRUE, data = stats_test) # studies report the participants have been diagnosed with ID
res_c <- rma.mv(yi, vi, random = list(~ 1 | effectsize_id, ~1 | study_id),
                          subset = group_inclusion_criteria == "group_c",
                          tdist = TRUE, data = stats_test) # studies only reports the mean IQ score lower than 60
res_d <- rma.mv(yi, vi, random = list(~ 1 | effectsize_id, ~1 | study_id),
                          subset = group_inclusion_criteria == "group_d",
                          tdist = TRUE, data = stats_test) # studies report ID diagnosis and eligible IQ scores

dat.comp.incl <- data.frame(alloc    = c("group_a", "group_b", "group_c", "group_d"
                                    ), 
                       estimate = c(coef(res_a), coef(res_b), coef(res_c), coef(res_d)
                                    ), 
                       stderror = c(res_a$se, res_b$se, res_c$se, res_d$se
                                    ),
                       tau2     = c(res_a$tau2, res_b$tau2, res_c$tau2, res_d$tau2 
                                   )
                       )
dfround(dat.comp.incl, 3)

```

```{r publication-bias}

# contour enhanced funnel plot, funnel centered at 0
funnel_data <- funnel(res_inhibition, level=c(90, 95, 99), refline=0, legend=TRUE)

# p-curve, R-Index are calculated in the Shiny App, .csv file with necessary data is on OSF. Link to the p-checker: https://shiny.psy.lmu.de/felix/p-checker/

# z-curve
zdata <- data.frame(z = stats_test$yi / sqrt(stats_test$vi),
                    p = 2 * pnorm(-abs(stats_test$yi / sqrt(stats_test$vi))))
fit <- zcurve(as.numeric(zdata[,"z"]))
summary(fit)
plot(fit)

#pet-peese: code modified from https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/pub-bias.html#small-study-effects
dat.petpeese <- data.frame(TE = stats_test$yi,
                           seTE_c = sqrt((stats_test$n_id+stats_test$n_magroup)/(stats_test$n_id*stats_test$n_magroup)),
                           seTE_c2 = (stats_test$n_id+stats_test$n_magroup)/(stats_test$n_id*stats_test$n_magroup))

pet <- rma.mv(TE, seTE_c2, mods = ~seTE_c, data = dat.petpeese, method = "FE")
peese <- rma.mv(TE, seTE_c2, mods = ~seTE_c2, data = dat.petpeese, method = "FE")

```


```{r}
sessionInfo()
```
